Spitzer, Gaia and the Potential of the Milky Way

### 2013-07-27 text/paper1/paper.tex
revisions

[TODO: this paragraph needs work]
There are two other apparent strengths of the method which require further investigation.
First it appears applicable to any debris that is known to come from a single object, and not restricted only to the very coldest tidal streams. For example, in principle the
method could  applied to the vast debris {\it clouds} that have been discovered subtending hundreds-thousands square degrees \citep[e.g. the Triangulum Andromeda
and Hercules-Aquila clouds]{rochapinto04,belokurov06}, or even stars that have only associations in orbital properties and do not form a coherent spatial structure
\citep[such as the angular momentum groupings in local giants found by][]{helmi99}.
Second, it appears trivial to combine constraints from multiple debris systems at once by simply integrating all debris from several satellites simultaneously with $D_{\rm
ps}$ defined appropriately for each star separately.

% this needs to go somewhere down here...
[This objective function is an approximation to a more general likelihood function, described in detail in forthcoming work (Price-Whelan \& Johnston in prep.). The results shown in sections xx and yy are meant to illustrate the strength and concept of the method..]

The limitations of the method also need to be understood. In particular, for the RR Lyraes associated with  the very coldest streams \citep[e.g. the globular clusters Pal5
and GD1][]{odenkirchen02,koposov10} the measurement errors are unlikely to be small enough for the
the differences in orbital properties to between debris and satellite to be detected, and the method should fail.

Lastly, the current version of the algorithm relies on accurate knowledge of the phase-space position of the parent satellite, which may not be available in some cases
\citep[for example, for the Orphan Stream][]{belokurov07}. Given sufficient data, position and motion of the original host could be solved for as additional free parameters,
but the effectiveness of this approach has yet to be investigated.

>>>>

[TODO: this paragraph needs work]
There are two other apparent strengths of the method which require further investigation.
\emph{The Rewinder} is applicable to any debris that is known to come from a single object, and not restricted only to the very coldest tidal streams. For example, in principle the
method could applied to the vast debris {\it clouds} that have been discovered subtending large solid angles \citep[e.g. the Triangulum Andromeda
and Hercules-Aquila clouds]{rochapinto04,belokurov06}, or even stars that have only associations in orbital properties and do not form a coherent spatial structure
\citep[such as the angular momentum groupings in local giants found by][]{helmi99}. Second, it appears trivial to combine constraints from multiple debris systems at once by simply integrating all debris from several satellites simultaneously with $D_{\rm ps}$ defined appropriately for each star separately.

[present the limitations]
The limitations of the method also need to be understood. Firstly, for the RR Lyraes associated with the very coldest streams \citep[e.g. the globular clusters Pal5
and GD1][]{odenkirchen02,koposov10} the measurement errors are unlikely to be small enough for the
the differences in orbital properties to between debris and satellite to be detected. [What will this cause? Maybe biases? One more sentence here]. Second, the method requires specifying a functional form for the potential. [...]. Lastly, the current version of the algorithm relies on accurate knowledge of the phase-space position of the parent satellite, which may not be available in some cases \citep[for example, for the Orphan Stream][]{belokurov07}.

[explain how some of them are handled automatically by the forthcoming machinery]
The objective function presented above is an approximation to a more general likelihood function, described in detail in forthcoming work (Price-Whelan \& Johnston in prep.). The results shown in sections xx and yy are meant to illustrate the strength and concept of the method.

Given sufficient data, position and motion of the original host could be solved for as additional free parameters,
but the effectiveness of this approach has yet to be investigated.
